Best Practices for Alchemical Free Energy Calculations [Article v \versionnumber]

### 2020-11-03 paper/manuscript.tex
fixing things that broke on merge

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{paper/figures/fig_pmf/pmf.png}
    \caption{{\bf Potential of mean force with respect to $\vec{\lambda}$ for TI and MBAR}
    The estimated PMF for a bound calculation of a Tyk2 ligand pair of the Wang et al.~\cite{wang2015accurate} with respect to $\vec{\lambda}$ estimated from TI and MBAR and showing agreement within errorbars. 
    }
    \label{fig:pmf}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.95\linewidth]{paper/figures/fig13_analysis_practices/Figure.png}
  \caption{\textbf{An example of recommended practices for graphing alchemical free energy predictions.} This figure shows the relation between predicted and experimentally-determined Gibbs free energy in kcal/mol with standard errors as error bars. The dark and light-orange regions depict the 1- and 2-kcal/mol confidence bounds. Statistical metrics for the data are reported, with 95\% confidence intervals determined by bootstrapping analysis. Extra care should be taken when investigating potential outliers further.}
   \label{fig:scatterplot_analysis}
\end{figure}

@@

\section*{Potentially Conflicting Interests}
%%%%%%%
%Declare any potentially competing interests, financial or otherwise
%%%%%%%
JM is a current member of the Scientific Advisory Board of Cresset. 
MK is employed by Cresset who commercially distribute a software for performing alchemical free energy calculations. MRS is a Open Science Fellow and consultant for Silicon Therapeutics.

\section*{Funding Information}
%%%%%%%
% Authors should acknowledge funding sources here. Reference specific grants.
%%%%%%%
ASJSM and JM acknowledge funding through an EPSRC flagship software grant: EP/P022138/1
MK and JM acknowledge funding through Innovate UK by KTP partnership 011120.
AR acknowledges partial support from the Tri-Institutional Program in Computational Biology and Medicine and the Sloan Kettering Institute.
HEBM acknowledges support from a Molecular Sciences Software Institute Investment Fellowship and Relay Therapeutics.
JDC is a current member of the Scientific Advisory Board of OpenEye Scientific Software and a consultant to Foresite Laboratories. A complete funding history for the Chodera lab can be found at \url{http://choderalab.org/funding}. 
DLM acknowledges support from the National Institutes of Health (R01GM108889, R01GM124270, and R01GM132386), and the National Science Foundation (CHE 1352608).
JDC acknowledges support from the National Institutes of Health (NIH P30 CA008748, NIH R01 GM121505, R01 GM132386).
The content is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{figures/fig_pmf/pmf.png}
    \caption{{\bf Potential of mean force with respect to $\vec{\lambda}$ for TI and MBAR}
    The estimated PMF for a bound calculation of a Tyk2 ligand pair of the Wang et al.~\cite{wang2015accurate} with respect to $\vec{\lambda}$ estimated from TI and MBAR and showing agreement within errorbars. 
    }
    \label{fig:pmf}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.95\linewidth]{figures/fig13_analysis_practices/Figure.png}
  \caption{\textbf{An example of recommended practices for graphing alchemical free energy predictions.} This figure shows the relation between predicted and experimentally-determined Gibbs free energy in kcal/mol with standard errors as error bars. The dark and light-orange regions depict the 1- and 2-kcal/mol confidence bounds. Statistical metrics for the data are reported, with 95\% confidence intervals determined by bootstrapping analysis. Extra care should be taken when investigating potential outliers further.}
   \label{fig:scatterplot_analysis}
\end{figure}

@@

\section*{Potentially Conflicting Interests}
%%%%%%%
%Declare any potentially competing interests, financial or otherwise
%%%%%%%
JM is a current member of the Scientific Advisory Board of Cresset. 
MK is employed by Cresset who commercially distribute a software for performing alchemical free energy calculations. MRS is a Open Science Fellow and consultant for Silicon Therapeutics. JDC is a current member of the Scientific Advisory Board of OpenEye Scientific Software and a consultant to Foresite Laboratories.

\section*{Funding Information}
%%%%%%%
% Authors should acknowledge funding sources here. Reference specific grants.
%%%%%%%
ASJSM and JM acknowledge funding through an EPSRC flagship software grant: EP/P022138/1
MK and JM acknowledge funding through Innovate UK by KTP partnership 011120.
AR acknowledges partial support from the Tri-Institutional Program in Computational Biology and Medicine and the Sloan Kettering Institute.
HEBM acknowledges support from a Molecular Sciences Software Institute Investment Fellowship and Relay Therapeutics.
A complete funding history for the Chodera lab can be found at \url{http://choderalab.org/funding}. 
DLM acknowledges support from the National Institutes of Health (R01GM108889, R01GM124270, and R01GM132386), and the National Science Foundation (CHE 1352608).
JDC acknowledges support from the National Institutes of Health (NIH P30 CA008748, NIH R01 GM121505, R01 GM132386).
The content is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.
